TODO

### 2024-12-13 code/expt_1/data_prep.Rmd
check all transcripts and rerun pre-processing

data_source <- "data/rounds.csv"
player_source <- "data/players.csv"

@@

games <- read_csv(here("data/games.csv"), col_types="ccc")|> filter(is.na(exclude)) |>  mutate(offset_sec=lubridate::ms(offset) |> lubridate::period_to_seconds()) |> select(-offset)

@@

wrangle_transcript <- function(game_num){
 read_csv(here("data/clean_transcripts", str_c(game_num,".csv")), show_col_types=F) |> 
  select(start, end, text, speaker, trial, role, echo, description, backchannel) |> 
    fill(trial) %>% 
  mutate(start=start/1000, end=end/1000) |> 
    nest(data=c(start, end, text, speaker, trial, role, echo, description, backchannel))
}

@@

stages <- read_csv(here("data/stages.csv")) |> select(index, gameId, startTimeAt) |> group_by(gameId)

@@

transcript_full <- timed_transcripts %>% select(-echo, -exclude) %>% left_join(echoes) %>% 
  left_join(trial_timing) %>% 
  rename(start_time=start, end_time=end) %>% 
  write_csv(here("data/timed_transcript.csv"))
```

@@

```{r}
transcript <- read_csv(here("data/timed_transcript.csv"))

dat <- read_csv(here("data/clean_data.csv")) %>% select(trial=trialNum, game, target, distractor)

transcript %>% filter(!is.na(description)) %>% group_by(trial, game) %>% 
  summarize(words=str_c(description, sep=" ", collapse=", ")) %>% left_join(dat) %>% write_csv(here("data/pre_sbert.csv"))

@@

```{r}
library(reticulate)
np <- import("numpy")
mat = np$load(here('data/post_sbert.npy'))
saveRDS(mat,here('data/post_sbert.RData'))
```

```{r}
sbert <- read_csv(here("data/pre_sbert.csv")) %>% bind_cols(read_rds(here("data/post_sbert.RData")) %>% 
  as_tibble())

@@

similarities <- M_mat %>%
    mutate(combinedId=str_c(game,trial,sep="_")) %>%
    make_across_df(F_mat, 'cosine') %>%
    separate(dim1, into=c("game1","trial1"), convert=T, sep="_") %>%
    separate(dim2, into=c("game2","trial2"), convert=T, sep="_") %>%
    mutate(sim = ifelse(is.nan(sim), NA, sim)) %>% write_rds(here("data/similarities.rds"))

>>>>

data_source <- "data/expt_1/rounds.csv"
player_source <- "data/expt_1/players.csv"

@@

games <- read_csv(here("data/expt_1/games.csv"), col_types="ccc")|> filter(is.na(exclude)) |>  mutate(offset_sec=lubridate::ms(offset) |> lubridate::period_to_seconds()) |> select(-offset)

@@

wrangle_transcript <- function(game_num){
 read_csv(here("data/expt_1/clean_transcripts", str_c(game_num,".csv")), show_col_types=F) |> 
  select(start, end, text, speaker, trial, role, echo, description, backchannel) |> 
    fill(trial) %>% 
  mutate(start=start/1000, end=end/1000) |> 
    nest(data=c(start, end, text, speaker, trial, role, echo, description, backchannel))
}

@@

stages <- read_csv(here("data/expt_1/stages.csv")) |> select(index, gameId, startTimeAt) |> group_by(gameId)

@@

transcript_full <- timed_transcripts %>% select(-echo, -exclude) %>% left_join(echoes) %>% 
  left_join(trial_timing) %>% 
  rename(start_time=start, end_time=end) %>% 
  write_csv(here("data/expt_1/timed_transcript.csv"))
```

@@

```{r}
transcript <- read_csv(here("data/expt_1/timed_transcript.csv"))

dat <- read_csv(here("data/expt_1/clean_data.csv")) %>% select(trial=trialNum, game, target, distractor)

transcript %>% filter(!is.na(description)) %>% group_by(trial, game) %>% 
  summarize(words=str_c(description, sep=" ", collapse=", ")) %>% left_join(dat) %>% write_csv(here("data/expt_1/pre_sbert.csv"))

@@

```{r}
library(reticulate)
np <- import("numpy")
mat = np$load(here('data/expt_1/post_sbert.npy'))
saveRDS(mat,here('data/expt_1/post_sbert.RData'))
```

```{r}
sbert <- read_csv(here("data/expt_1/pre_sbert.csv")) %>% bind_cols(read_rds(here("data/expt_1/post_sbert.RData")) %>% 
  as_tibble())

@@

similarities <- M_mat %>%
    mutate(combinedId=str_c(game,trial,sep="_")) %>%
    make_across_df(F_mat, 'cosine') %>%
    separate(dim1, into=c("game1","trial1"), convert=T, sep="_") %>%
    separate(dim2, into=c("game2","trial2"), convert=T, sep="_") %>%
    mutate(sim = ifelse(is.nan(sim), NA, sim)) %>% write_rds(here("data/expt_1/similarities.rds"))

### 2024-12-13 write-ups/kid_tangrams_cogsci_2025/kid_tangrams_cogsci_2025.Rmd
check all transcripts and rerun pre-processing

* Check transcription for expt 1 and 2 especially for ref expression

* Rerun sbert stuff

@@

@@

## Participants
Experiment 2 was run between March and August of 2024, at the same university preschool. No children participated in both experiments. ZZ pairs of children completed all 16 critical trials, and YY pairs of children completed between 8 and 16 critical trials.

>>>>

* Rerun [re-processing 
sbert stuff

@@

* fix transcripts to have kid ids that are more consistent (not pear123)

* are there analyses to link success with description sticking (do successful descriptions stick more)

* qual description of different ways kids do coordinate with each other

* do we want to meta-analyze at all

* get age range mean and gender distributions!

* mention that we post-hoc excluded trials where we couldn't transcript any speaker description (either didn't happen or completely unintelligible)

@@

## Participants
Experiment 2 was run between March and August of 2024, at the same university preschool. No children participated in both experiments. ZZ pairs of children completed all 16 critical trials, and YY pairs of children completed between 8 and 16 critical trials. TODO mention that one kid was actually too young
